### 2011-06-15 Spatial_adaptation/panmixia.tex
/* Comparison to panmixia */ captions.

For the third question,
to get an idea we can use the results on standing variation,
and treat the mutations arising while the first is fixing, if such exist, as ``standing variation''.
This means setting 
\[
  \lambda_0 = 4 \rho \mu s T_l = 4 \rho \mu \log(\sigma^2 \rho) .
\]
Recall the characteristic length solves $\lambda_0 \pi \chi^2 + \lambda \pi \chi^3/v = 1$.
Set $\chi_0 = 1/\sqrt{\pi \lambda_0}$, 
the characteristic length only from the mutations arising while the first fixes locally;
we are interested in the numbers of mutations arising relative to these,
which is about $x=(\chi/\chi_0)^2$.
This proportion is between zero and one and satisfies
$x = 1-\gamma x^{3/2}$, 
where 
\[
  \gamma = \frac{ \sqrt{s} }{ \sigma \sqrt{4 \pi \rho \mu} \log^{3/2}(\sigma^2 \rho) } .
\]
The relationship between $\gamma$ and $f$ is shown in this figure:

\includegraphics[width=1.0\textwidth]{f-versus-gamma.pdf}

showing that if $\gamma>1$ then $f$ drops off quickly.
If we then fix $\mu=10^{-8}$ and $\rho=1$ (working in units of $1/\sqrt{\rho}$), 
then we get the following picture of $\log \gamma$:

\includegraphics[width=0.8\textwidth]{gamma-contour-1e-8.pdf}

>>>>

For the third question,
to get an idea we can use the results on standing variation,
and treat the mutations arising while the first is fixing, if such exist, as ``standing variation''.
This means setting 
\[
  \lambda_0 = 4 \rho \mu s T_l = 4 \rho \mu \log(\sigma^2 \rho) .
\]
Recall the characteristic length solves $\lambda_0 \pi \chi^2 + \lambda \pi \chi^3/v = 1$.
Set $\chi_0 = 1/\sqrt{\pi \lambda_0}$, 
the characteristic length only from the mutations arising while the first fixes locally;
we are interested in the numbers of mutations arising relative to these,
which is about $x=(\chi/\chi_0)^2$.
This proportion is between zero and one and satisfies
$x = 1-\gamma x^{3/2}$, 
where 
\[
  \gamma = \frac{ \sqrt{s} }{ \sigma \sqrt{4 \pi \rho \mu} \log^{3/2}(\sigma^2 \rho) } .
\]
The relationship between $\gamma$ and $x$ is shown in this figure:

\begin{figure}[h!]
\includegraphics[width=1.0\textwidth]{f-versus-gamma.pdf}
\caption{ Proportion difference in numbers of mutations ($x$) versus $\gamma$, on a log-log scale. }
\end{figure}

showing that if $\gamma>1$ then $x$ drops off quickly.
If we then fix $\mu=10^{-8}$ and $\rho=1$ (working in units of $1/\sqrt{\rho}$), 
then we get the following picture of $\log \gamma$:

\begin{figure}[h!]
\includegraphics[width=0.8\textwidth]{gamma-contour-1e-8.pdf}
\caption{ Contour plot of $\log\gamma$ as a function of $s$ and $\sigma$. }
\end{figure}
